Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-13 paper.tex
Pb dual
update

\author{
Alexis THIBAULT\\
\'Ecole Normale Sup\'erieure\\
Paris, France\\
\texttt{alexis.thibault@ens.fr}
 \And
L\'enaic CHIZAT\\
\'Ecole Normale Sup\'erieure\\ Paris Dauphine (PSL research University)\\
Paris, France\\
\texttt{lenaic.chizat@ens.fr}
 \AND
Charles DOSSAL\\
INSA Toulouse\\
Institut de Math\'ematiques de Toulouse\\
Toulouse,  France\\
\texttt{dossal@insa-toulouse.fr}
\And 
Nicolas PAPADAKIS\\
CNRS, Institut de Math\'ematiques de Bordeaux\\
Talence, France\\
\texttt{nicolas.papadakis@math.u-bordeaux.fr}
} 
% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

@@

\begin{theorem}
	Let $\theta$ and $\omega$ be such that $1\le \theta < \omega < 2$. Let $U$ be the open set defined by:
	\begin{equation}\label{eq:open_set_U}
	U = \left\{
	\gamma \in \IR_{+*}^{nm} \mid
	F(P^\omega_{\Ccal_1}(\gamma)) < F(\gamma)
	\text{ and }
	F(P^\omega_{\Ccal_2}(P^\theta_{\Ccal_1}(\gamma))) < F(P^\theta_{\Ccal_1}(\gamma))
	\right\}.
	\end{equation}
	Set the initial value $\gamma^0 = e^{-c/\epsilon}$, and iterate:
	\begin{align*}
	\gamma^{l+1} =
	\begin{cases}
	P^\theta_{\Ccal_2}(P^\theta_{\Ccal_1}(\gamma^l)) & \text{if } \gamma \in U \\
	P_{\Ccal_2}(P_{\Ccal_1}(\gamma^l)) & \text{otherwise.}
	\end{cases}
	\end{align*}
	Then the iterates $(\gamma^l)$ converge to $\gamma^*$.
\end{theorem}
{\color{red} 
	In practice the test would be: check whether the $\omega$-relaxed projection of $\zeta$ on $\Ccal_1$ decreases the value of
	$F$; if so, calculate $P_{\Ccal_1}^\theta(\zeta)$ (don't update $\zeta$ yet) and check that its $\omega$-relaxed projection on $\Ccal_2$ decreases the value of $F$ again. \\
	$\longrightarrow$ Has to calculate 3 projections sometimes. This result is weaker than the one from my report, but easier to prove. Maybe we could avoid having $U$, and rather perform the test independently on each variable ? (Or we could find a cheaper test).}
\begin{remark}
	Given lemma \ref{lemma:lyapunov_decrease}, it can be seen that $\gamma^* \in U$. Therefore, iterations eventually all use the over-relaxed operators.
\end{remark}
{\color{blue} It could be good to show on typical experiments how many times the test fails. If the test never fails after a few iterations, we could justify that doing a few Sinkhorn iteration and then always the over-relaxed algorithm is fine in practice.}

@@

\section{Local rate of convergence ?}
Some material for adapting Lenaic results:

@@

\section{Conclusion}

>>>>

%
\author{
Alexis THIBAULT\\
\'Ecole Normale Sup\'erieure\\
Paris, France\\
\texttt{alexis.thibault@ens.fr}
 \And
L\'enaic CHIZAT\\
\'Ecole Normale Sup\'erieure\\ Paris Dauphine (PSL research University)\\
Paris, France\\
\texttt{lenaic.chizat@ens.fr}
 \AND
Charles DOSSAL\\
INSA Toulouse\\
Institut de Math\'ematiques de Toulouse\\
Toulouse,  France\\
\texttt{dossal@insa-toulouse.fr}
\And 
Nicolas PAPADAKIS\\
CNRS, Institut de Math\'ematiques de Bordeaux\\
Talence, France\\
\texttt{nicolas.papadakis@math.u-bordeaux.fr}
} 
% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

@@

\begin{theorem}
	Let $\theta$ and $\omega$ be such that $1\le \theta < \omega < 2$. Let $U$ be the open set defined by:
	\begin{equation}\label{eq:open_set_U}
	U = \left\{
	\gamma \in \IR_{+*}^{nm} \mid
	F(P^\omega_{\Ccal_1}(\gamma)) < F(\gamma)
	\text{ and }
	F(P^\omega_{\Ccal_2}(P^\theta_{\Ccal_1}(\gamma))) < F(P^\theta_{\Ccal_1}(\gamma))
	\right\}.
	\end{equation}
	Set the initial value $\gamma^0 = e^{-c/\epsilon}$, and iterate:
	\begin{align*}
	\gamma^{l+1} =
	\begin{cases}
	P^\theta_{\Ccal_2}(P^\theta_{\Ccal_1}(\gamma^l)) & \text{if } \gamma \in U \\
	P_{\Ccal_2}(P_{\Ccal_1}(\gamma^l)) & \text{otherwise.}
	\end{cases}
	\end{align*}
	Then the iterates $(\gamma^l)$ converge to $\gamma^*$.
\end{theorem}
{\color{red} 
	In practice the test would be: check whether the $\omega$-relaxed projection of $\zeta$ on $\Ccal_1$ decreases the value of
	$F$; if so, calculate $P_{\Ccal_1}^\theta(\zeta)$ (don't update $\zeta$ yet) and check that its $\omega$-relaxed projection on $\Ccal_2$ decreases the value of $F$ again. \\
	$\longrightarrow$ Has to calculate 3 projections sometimes. This result is weaker than the one from my report, but easier to prove. Maybe we could avoid having $U$, and rather perform the test independently on each variable ? (Or we could find a cheaper test).}
\begin{remark}
	Given lemma \ref{lemma:lyapunov_decrease}, it can be seen that $\gamma^* \in U$. Therefore, iterations eventually all use the over-relaxed operators.

\end{remark}
{\color{blue} As the inequality is strict in U, $\gamma^*\notin U$.}

@@

\section{Local rate of convergence ?}
Some material to adapt Lenaic results:

@@

\section{Conclusion and perspectives}
